---
title: "Toxicity Analysis"
author: "Casey Bray"
date: "2022-11-25"
output: pdf_document
---

Toxic Dataset: "https://archive-beta.ics.uci.edu/dataset/728/toxicity-2"

```{r Libraries, echo=FALSE, warnings=FALSE}
library('tidyverse') ## Data Manipulation.
library("caret") ## RFE or 'Recursive Feature Elimination'.
library("randomForest") ## To implement Random Forest Model.
library("gridExtra") ## Plot multiple ggplot graphs side-by-side.
library("ggplot2") ## Plotting package.
```


```{r Data}
## Read in dataset to variable "toxic".
toxic <- read.csv("toxicity_data.csv")

## Create a backup of "toxic" dataset. 
toxic_copy1 <- toxic
```


```{r Target Variable}
## Quick review of target variable, "Class", shows that NonToxic is 2:1 to Toxic.
toxic %>%
  count(Class)
```

Due to the relative size of this dataset, 1204 variables, it is necessary to 
do some sort of feature selection first to reduce the dataset to a consumable
chunk of data.

--------------------------------------------------------------------------------

-- Recursive Feature Elimination:
 Also called 'RFE', is an algorithm used to select features that accuractely 
predict a 'target' variable in prediction models. RFE utilizes a backward 
selection process to select features. The steps are as follows:

  1. Builds model & calculates importance of all features(except 'target').
  
  2. Rank-orders features and removes ones with least importance one-by-one
     based on model eval metrics(RMSE,accuracy,kappa).
     
  3. Repeats process until a <i>smaller</i> set of features is achieved. 
  
** Model can select ALL features.
** Feature selection can also be based on model or criterion(e.g., accuracy).


```{r Feature Selection}
## First, we need to split data into train/test sets.
sample <- sample(c(TRUE,FALSE), nrow(toxic), replace = TRUE, prob=c(0.7,0.3))
train <- toxic[sample, ]
test <- toxic[!sample, ]

## Define our recursive feature elimination
control_rfe = rfeControl(functions = rfFuncs, # random forest
                      method = "repeatedcv", # repeated cv
                      repeats = 5, # number of repeats
                      number = 10) # number of folds

set.seed(50) ## for reproducibility

# Performing RFE, this may take some time
result_rfe = rfe(x = train[,-1204], 
                 y = as.factor(unlist(train[,1204])), 
                 sizes = c(1:15),
                 rfeControl = control_rfe)


print(result_rfe)
```

```{r Selected Features, warning=FALSE}
## Show our selected features.
predictors(result_rfe)


## Provide a visual version of the selected features. I have subsetted the 
## results as the before graph was very difficult to interpret.
plt1 <- ggplot(data = result_rfe, metric = "Accuracy") + xlim(0,25)
plt2 <- ggplot(data = result_rfe, metric = "Kappa") + xlim(0,25) 

grid.arrange(plt1,plt2,ncol=2,top="RFE Accuracy & Kappa Results")
```

As seen above, we decided to limit the features to ~15 variables. RFE, or 
"Recursive Feature Elimination", selected 8 as it yields the highest 
accuracy from cross-validation. This should greatly improve model interpretability
in the future. 

```{r Subset Data with Selected Features}
## Let's first subset the data with our chosen features.
final_toxic <- select(toxic,"MATS6c","MDEC.23","SpMax3_Bhm","ZMIC1","WTPT.5",
                      "AATSC2e","GATS5c","ATSC3v","Class") 

## Preview our new data.
str(final_toxic)
```

--------------------------------------------------------------------------------

Feature Exploration:

```{r MATS6c}
## MATS6c evaluation
ggplot(final_toxic, aes(x=Class, y=MATS6c, fill=Class, trim=FALSE)) +
  geom_violin(width=0.8) +
  geom_boxplot(width=0.2,color='black') +
  ggtitle("Violin plot of MATS6c by Class")

## MDEC.23 evaluation
ggplot(final_toxic, aes(x=Class, y=MDEC.23, fill=Class, trim=FALSE)) +
  geom_violin(width=0.8) +
  geom_boxplot(width=0.2,color='black') +
  ggtitle("Violin plot of MDEC.23 by Class")

## SpMax3_Bhm evaluation
ggplot(final_toxic, aes(x=Class, y=SpMax3_Bhm, fill=Class, trim=FALSE)) +
  geom_violin(width=0.8) +
  geom_boxplot(width=0.2,color='black') +
  ggtitle("Violin plot of SpMax3_Bhm by Class")

## ZMIC1 evaluation
ggplot(final_toxic, aes(x=Class, y=ZMIC1, fill=Class, trim=FALSE)) +
  geom_violin(width=0.8) +
  geom_boxplot(width=0.2,color='black') +
  ggtitle("Violin plot of ZMIC1 by Class")

## WTPT.5 evaluation
ggplot(final_toxic, aes(x=Class, y=WTPT.5  , fill=Class, trim=FALSE)) +
  geom_violin(width=0.8) +
  geom_boxplot(width=0.2,color='black') +
  ggtitle("Violin plot of WTPT.5   by Class")

## AATSC2e evaluation
ggplot(final_toxic, aes(x=Class, y=AATSC2e, fill=Class, trim=FALSE)) +
  geom_violin(width=0.8) +
  geom_boxplot(width=0.2,color='black') +
  ggtitle("Violin plot of AATSC2e by Class")
```
-- MATS6c appears to have a much wider distribution compared to non-toxic. 
However, median values appear to be quite similar. Although, Toxic median comes
out just a shade higher! Neither show a normal distribution and have apparent 
tails on the high end.


-- MDEC.23 shows quite a visible difference between Toxic median and Non-Toxic 
median! Toxic also shows a much more narrow distribution and fewer outliers.


-- SpMax3_Bhm shows quite an interesting spread! The outliers are quite unusual 
and very far from the IQR(Interquartile Range). Outliers aside, distribution 
shows a very normalized shape for both classes. Toxic, however, has a lower 
median with what appears to be a quite large Upper Quartile.


-- ZMIC1 shows a very spread out distribution for both Classes. On a positive 
note, Toxic shows what appears to be a very significantly different median from
Non-Toxic. Toxic also presents a much larger lower quartile and significant 
outliers.


-- WTPT.5  appears to show similar medians for both classes. Toxic shows a larger 
lower quartile while Non-Toxic shows a large Upper quartile. Both Classes have a
very large distribution.


-- AATSC2e shows both classes have a very narrow distrbution. Non-Toxic has a 
slightly higher median value. Toxic has a very large outlier. However, we have
no way to verify this is a typo or not. 


--------------------------------------------------------------------------------

Decision Tree:

```{r Train/Test Split}
train_control <- trainControl(method = "LOOCV")

set.seed(42)
sample <- sample(c(TRUE,FALSE), nrow(final_toxic), replace = TRUE, prob=c(0.7,0.3))
train_toxic <- final_toxic[sample, ]
test_toxic <- final_toxic[!sample, ]


dim(train_toxic)
dim(test_toxic)
```


```{r Random Forest}
## Decision Tree using "Caret"
toxic.tree = train(Class ~ ., 
                  data=train_toxic, 
                  method="rpart", 
                  trControl = train_control)

print(toxic.tree)


toxic.pred <- predict(toxic.tree, newdata = test_toxic)

cat("\nPrediction Table: ")
table(toxic.pred, test_toxic$Class)

cat("\nError Rate: ")
round(mean(toxic.pred != test_toxic$Class),2)
```

```{r Tree Plot, warning=FALSE}
suppressMessages(library(rattle))

fancyRpartPlot(toxic.tree$finalModel)
```

--------------------------------------------------------------------------------

Random Forest:

```{r}
set.seed(55)
## Set our number of variables to be randomly collected
mtries <- sqrt(ncol(train_toxic))
grid <- expand.grid(.mtry=mtries)

## Assign random forest model to variable.
toxic.tree = train(Class ~ ., 
                  data=train_toxic, 
                  method="rf", 
                  metric="Accuracy",
                  tuneGrid = grid,
                  trControl = train_control)

print(toxic.tree)
```

```{r Forest Predictions}
toxic.pred <- predict(toxic.tree, newdata = test_toxic)

cat("\nPrediction Table: ")
table(toxic.pred, test_toxic$Class)

cat("\nError Rate: ")
round(mean(toxic.pred != test_toxic$Class),2)


```
Random Forest reduces test error from 0.39 to 0.32 — a 7-percentage-point absolute improvement over the single Decision Tree baseline.

----------------------------------------